Online Verification of Commutativity

### 2020-09-04 acmPaper/paper.tex
added statement about profiling results

The na\"{i}ve baseline performs poorly, taking well over a thousand seconds for even small graphs of 10 nodes.
The batch algorithm brings timing down to seconds.
\ref{algo_online_polynomial} performs only slightly better.
Surprisingly, the optimal set algorithm cuts time cost by several orders of magnitude, and runs in milliseconds for small graphs.
All implementations are sensitive to density, performing better when density is very low or very high.

>>>>

The na\"{i}ve baseline performs poorly, taking well over a thousand seconds for even small graphs of 10 nodes.
The batch algorithm brings timing down to seconds.
However time cost still does not scale very well, with computation for a graph with 14 nodes and 0.4 density taking hours.
Our implementation does not memoize the construction of the vector and matrix representation of paths in GF(2).
Profiling reveals that this vector construction step is called many times and is chiefly responsible for the high time cost.
\ref{algo_online_polynomial} performs only slightly better.
Surprisingly, the optimal set algorithm cuts time cost by several orders of magnitude, and runs in milliseconds for small graphs.
All implementations are sensitive to density, performing better when density is very low or very high.
